A quantitative analysis of Media Agenda and Public Opinion using time-evolving topic distribution

### 2018-09-04 bmc_article.tex
Desarrollo de la primera parte

% Agenda Setting Theory
\par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
In the seminal study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that the aspects of public affairs that are prominent in the news become prominent in the public. This work is considered the founding of the agenda-setting theory.
In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
For instance, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.

>>>>

% Agenda Setting Theory
\par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
In the seminal study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that the aspects of public affairs that are prominent in the news become prominent in the public. This work is considered the founding of the agenda-setting theory.
In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda: The topics that the public consider as priority.
For instance, it explores how media content correlate with audiences of different ages \cite{coleman2007young} and how people agendas differ based on the way they consume news \cite{althaus2002agenda}.
On the other hand, the theory hypothesizes how the media affect the audience opinion, for instance, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
Related to our work, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
